p-adic stability in linear algebra

### 2015-04-12 examples/stability.tex
Notes to David on where to insert additional info requested by referee

The aim of this section is to briefly summarize the content of 
\cite{caruso-roe-vaccon:14a} and fill in certain details.

@@

Proposition \ref{prop:precision} can be rephrased in terms of precision 
as follows: if the input $v_0$ is known at precision $H$, then $f(v_0)$ 
is known up to $f'(v_0)(H)$ and this precision is optimal. Optimality is 
reflected by the equality sign in Eq.~\eqref{eq:firstorder}.

@@

\begin{deftn} \label{def:diffused}
If $H \subset E$ is a lattice, let
\[
H_0 = \pi_1(H) \oplus \cdots \oplus \pi_n(H).
\]
Set $k = \text{length}(H_0/H)$.  Then we say that $H$ has $k$
\emph{diffused digits of precision}.
\end{deftn}
If $H$ represents the actual precision of some object, then
$H_0$ is the best coordinate-wise approximation to $H$.
The diffused precision is not visible coordinate-wise in the
specified basis of $E$.

>>>>

The aim of this section is to briefly summarize the content of 
\cite{caruso-roe-vaccon:14a} and fill in certain details. % Add usual way to track precision.

@@

Proposition \ref{prop:precision} can be rephrased in terms of precision 
as follows: if the input $v_0$ is known at precision $H$, then $f(v_0)$ 
is known up to $f'(v_0)(H)$ and this precision is optimal. Optimality is 
reflected by the equality sign in Eq.~\eqref{eq:firstorder}. % define coordinate-wise and lattice-wise here.

@@

\begin{deftn} \label{def:diffused}
If $H \subset E$ is a lattice, let
\[
H_0 = \pi_1(H) \oplus \cdots \oplus \pi_n(H).
\]
Set $k = \text{length}(H_0/H)$.  Then we say that $H$ has $k$
\emph{diffused digits of precision}.
\end{deftn} % Add explanation here - smallest lattice containing H here.
If $H$ represents the actual precision of some object, then
$H_0$ is the best coordinate-wise approximation to $H$.
The diffused precision is not visible coordinate-wise in the
specified basis of $E$.
